---
title: "Developing Data Products: Week 4 Course Project"
date: "March 14, 2018"
output: ioslides_presentation
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(quantmod)
```


## Technical Analysis Of Stocks

### Overview 
Technical analysis uses statistical techniques to analyze a stock's historic price movements in order to determine the probability of the future price of the stock.

Statistical analysis of stock prices has resulted in numerous technical indicators that are used extensively by traders to perform technical analysis. 

Click link below my example on Technical Analysis. 
https://tashscrnlg.shinyapps.io/stkApp/


## Technical Indicators

### Popular Technical Indicators

Simple Moving Average (SMA): Track the average of a stock price over a pre-defined period. Popular periods are 200, 100, 50, 20, 10, and 5 days. 
Investopedia for more info: https://www.investopedia.com/terms/s/sma.asp

Relative Strength Indicator (RSI): 

The RSI is one of the most widely-known technical indicators with many traders using it both 
to identify overbought and oversold conditions as well as to measure the strength of a trend. 
Investopedia for more info: (https://www.investopedia.com/terms/r/rsi.asp)

Bollinger Bands:
Tracks the price movement of a stock's price in a band that is two standard deviation from 
the stock's 21 days moving average. 
Investopedia for more info: https://www.investopedia.com/terms/b/bollingerbands.asp

## Getting Stock Data in R

To obtain stock data for analysis in R requires the quantmod package that is avaiable on CRAN.
This package have many function and features and includes:

Downloading of  hisoric stock prices from YAHOO or GOOGLE;
Charting of stock data;
Adding technical indicators to charts

For more information on quantmod vist the site https://www.quantmod.com/


## How to Retrieve Stock Data


### Use the getSymbols function to retrieve data from yahoo or google. 

```{r, comment="", echo=TRUE}
      data <- getSymbols("MSFT", src = "yahoo", 
                               from = Sys.Date()-90,
                               to = Sys.Date(),
                               auto.assign = FALSE, warnings=FALSE)
```

## Example Stock Data - Microsoft (MSFT)

 

```{r, comment="", echo=TRUE}
      tail(data)
```

